Structured Versus Decorated Cospans

### 2020-12-09 cospans.tex
work on Lemma 3.4 - Lemma 3.6

% Structured and decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2020/12/8

@@

\item a functor $H \maps \A \to \A'$ that preserves finite limits.

@@

\item an isomorphism $\theta \maps EF \Rightarrow F'H$: {\chris is this natural or pseudonatural? It should be clarified.}

@@

\item The image of an object $a \in F\lCsp_0=\A$ is the object $H(a) \in F'\lCsp_0=\A'$,

@@

where given a decoration morphism $\tau \colon F(h)(x) \to x'$, the induced decoration morphism is:

@@

{\chris There should be an iso on the right if we go with pseudonatural isomorphism}

@@

%Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F' \maps \mathsf{A'} \to \Cat$%, we can obtain another symmetric monoidal double category $F' \lCsp$.
%a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\H \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\H_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\H_1$ defined on horizontal 1-cells by:
%We define the object component $\lH_0$ to be $H$ and define the arrow component $\lH_1$ on horizontal 1-cells by:
%\node (B) at (1,0) {$c$};
%\node (D) at (1,-0.5) {$d \in F(c)$};
%\node (B') at (4.5,0) {$H(c)$};
%\node (D') at (4.5,-0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
%and on 2-morphisms by:
%\node (A) at (0,0.5) {$a$};
%\node (A') at (0,-0.5) {$a'$};
%\node (B) at (1,0.5) {$c$};
%\node (C) at (2,0.5) {$b$};
%\node (C') at (2,-0.5) {$b'$};
%\node (D) at (1,-0.5) {$c'$};
%\node (E) at (3,0.5) {$d \in F(c)$};
%\node (F) at (3,-0.5) {$d' \in F(c')$};
%\node (G) at (1,-1) {$\tau \maps F(h)(d) \to d'$};
%\node (A'') at (4.25,0.5) {$H(a)$};
%\node (A''') at (4.25,-0.5) {$H(a')$};
%\node (B'') at (5.25,0.5) {$H(c)$};
%\node (C'') at (6.25,0.5) {$H(b)$};
%\node (C''') at (6.25,-0.5) {$H(b')$};
%\node (D'') at (5.25,-0.5) {$H(c')$};
%\node (E'') at (8,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
%\node (F'') at (8,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
%\node (G'') at (5.25,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d')\phi)$};
%\node (H) at (3.5,0) {$\mapsto$};
%(A) edge node[above]{$$} (B)
%(C) edge node[above]{$$} (B)
%(A) edge node[left]{$f$} (A')
%(C) edge node[right]{$g$} (C')
%(A') edge node {$$} (D)
%(C') edge node {$$} (D)
%(B) edge node [left] {$h$} (D)
%(A'') edge node[above]{$$} (B'')
%(C'') edge node[above]{$$} (B'')
%(A'') edge node[left]{$H(f)$} (A''')
%(C'') edge node[right]{$H(g)$} (C''')
%(A''') edge node {$$} (D'')
%(C''') edge node {$$} (D'')
%(B'') edge node [left] {$H(h)$} (D'');
%where $E \maps \Cat \to \Cat$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \maps EF \Rightarrow F'H$:
%\node (A) at (0,0) {$\A$};
%\node (B) at (1,0) {$\Cat$};
%\node (C) at (0,-1) {$\mathsf{A'}$};
%\node (D) at (1,-1) {$\Cat$};
%\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
%(A) edge node[above]{$F$} (B)
%(A) edge node[left]{$H$} (C)
%(B) edge node[right]{$E$} (D)
%(C) edge node[above]{$F'$} (D);
Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\tau \maps F(h)(d) \to d'$ of $F(c')$ as a natural transformation  in $\Cat$:
\node (A) at (0,-0.5) {$1$};
\node (B) at (1,0) {$F(c)$};
\node (D) at (1,-1) {$F(c')$};
\node (C) at (0.75,-0.5) {$\Swarrow \tau$};
(A) edge node[above]{$d$} (B)
(A) edge node[below]{$d'$} (D)
(B) edge node[right]{$F(h)$} (D);
Applying the symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ to this diagram yields:
\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
\node (B) at (2,0) {$E(F(c))$};
\node (D) at (2,-1) {$E(F(c'))$};
\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
(A) edge node[above]{$E(d)$} (B)
(A) edge node[below]{$E(d')$} (D)
(B) edge node[right]{$E(F(h))$} (D);
Then because the above square commutes up to the isomorphism $\theta \maps EF \Rightarrow F'H$, we get:
\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
\node (B) at (2,0) {$E(F(c))$};
\node (D) at (2,-1) {$E(F(c'))$};
\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
\node (E) at (4,0) {$F'(H(c))$};
\node (F) at (4,-1) {$F'(H(c'))$};
(B) edge node [above] {$\theta_c$} (E)
(D) edge node [above] {$\theta_{c'}$} (F)
(A) edge node[above]{$E(d)$} (B)
(A) edge node[below]{$E(d')$} (D)
which results in a 2-morphism $E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$ in $F'(H(c'))$. To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\lCsp$:
\node (B) at (1.5,0.5) {$c$};
\node (C) at (3,0.5) {$b$};
\node (C') at (3,-0.5) {$b'$};
\node (D) at (1.5,-0.5) {$c'$};
\node (E) at (4.5,0.5) {$d \in F(c)$};
\node (F) at (4.5,-0.5) {$d' \in F(c')$};
\node (G) at (1.5,-1) {$\tau \maps F(h)(d) \to d'$};
\node (A'') at (0,-1.5) {$a'$};
\node (A''') at (0,-2.5) {$a''$};
\node (B'') at (1.5,-1.5) {$c'$};
\node (C'') at (3,-1.5) {$b'$};
\node (C''') at (3,-2.5) {$b''$};
\node (D'') at (1.5,-2.5) {$c''$};
\node (E'') at (4.5,-1.5) {$d' \in F(c')$};
\node (F'') at (4.5,-2.5) {$d'' \in F(c'')$};
\node (G'') at (1.5,-3) {$\tau' \maps F(h')(d') \to d''$};
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(A'') edge node[above]{$$} (B'')
(C'') edge node[above]{$$} (B'')
(A'') edge node[left]{$f'$} (A''')
(C'') edge node[right]{$g'$} (C''')
(A''') edge node [above]{$$} (D'')
(C''') edge node [above]{$$} (D'')
(B'') edge node [left] {$h'$} (D'');
if we first compose these, the result is:
\node (A') at (0,-0.5) {$a''$};
\node (B) at (1.5,0.5) {$c$};
\node (C) at (3,0.5) {$b$};
\node (C') at (3,-0.5) {$b''$};
\node (D) at (1.5,-0.5) {$c''$};
\node (E) at (4.5,0.5) {$d \in F(c)$};
\node (F) at (4.5,-0.5) {$d'' \in F(c'')$};
\node (G) at (1.5,-1) {$\tau ' \tau \maps F(h' h)(d) \to d''$};
(A) edge node[left]{$f' f$} (A')
(C) edge node[right]{$g' g$} (C')
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(B) edge node [left] {$h' h$} (D);
and then the image of this 2-morphism under the double functor $\H$ is given by:
and then the image of this 2-morphism under the double functor $\lH$ is given by:
\node (A) at (0,0.5) {$H(a)$};
\node (A') at (0,-0.5) {$H(a'')$};
\node (B) at (1.5,0.5) {$H(c)$};
\node (C) at (3,0.5) {$H(b)$};
\node (C') at (3,-0.5) {$H(b'')$};
\node (D) at (1.5,-0.5) {$H(c'')$};
\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
\node (G) at (1.5,-1) {$E(\tau ' \tau) \maps F'(H(h' h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
(A) edge node[left]{$H(f' f)$} (A')
(C) edge node[right]{$H(g' g)$} (C')
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(B) edge node [left] {$H(h' h)$} (D);
On the other hand, applying the double functor $\H$ first gives:
On the other hand, applying the double functor $\lH$ first gives:
\node (A) at (0,0.5) {$H(a)$};
\node (A') at (0,-0.5) {$H(a')$};
\node (B) at (1.5,0.5) {$H(c)$};
\node (C) at (3,0.5) {$H(b)$};
\node (C') at (3,-0.5) {$H(b')$};
\node (D) at (1.5,-0.5) {$H(c')$};
\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
\node (F) at (5,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
\node (G) at (1.5,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$};
\node (A'') at (0,-1.5) {$H(a')$};
\node (A''') at (0,-2.5) {$H(a'')$};
\node (B'') at (1.5,-1.5) {$H(c')$};
\node (C'') at (3,-1.5) {$H(b')$};
\node (C''') at (3,-2.5) {$H(b'')$};
\node (D'') at (1.5,-2.5) {$H(c'')$};
\node (E'') at (5,-1.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
\node (F'') at (5,-2.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
\node (G'') at (1.5,-3) {$E(\tau') \maps F'(H(h'))(\theta_{c'} E(d')\phi) \to (\theta_{c''}E(d'')\phi)$};
(A) edge node[left]{$H(f)$} (A')
(C) edge node[right]{$H(g)$} (C')
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(B) edge node [left] {$H(h)$} (D)
(A'') edge node[above]{$$} (B'')
(C'') edge node[above]{$$} (B'')
(A'') edge node[left]{$H(f')$} (A''')
(C'') edge node[right]{$H(g')$} (C''')
(A''') edge node [above]{$$} (D'')
(C''') edge node [above]{$$} (D'')
(B'') edge node [left] {$H(h')$} (D'');
and then composing these gives:
\node (A) at (0,0.5) {$H(a)$};
\node (A') at (0,-0.5) {$H(a'')$};
\node (B) at (1.5,0.5) {$H(c)$};
\node (C) at (3,0.5) {$H(b)$};
\node (C') at (3,-0.5) {$H(b'')$};
\node (D) at (1.5,-0.5) {$H(c'')$};
\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
\node (G) at (1.5,-1) {$E(\tau ' \tau) \maps F'(H(h' h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
(A) edge node[left]{$H(f' f)$} (A')
(C) edge node[right]{$H(g' g)$} (C')
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(B) edge node [left] {$H(h' h)$} (D);
This double functor $\H$ satisfies the equations $S \H_1 = HS$ and $T \H_1=HT$.
This double functor $\lH$ satisfies the equations $S \lH_1 = HS$ and $T \lH_1=HT$.

Given two composable horizontal 1-cells $M$ and $N$ in $F\lCsp$:
\node (B) at (1,0) {$c_1$};
\node (D) at (1,-0.5) {$d_M \in F(c_1)$};
\node (F) at (4,0) {$c_2$};
\node (G) at (5,0) {$a_2$};
\node (H) at (4,-0.5) {$d_N \in F(c_2)$};
composing first gives $M \odot N$:
\node (B) at (1.5,0) {$c_1+_b c_2$};
\node (C) at (3,0) {$a_2$};
\node (D) at (1.5,-0.5) {$d_{M \odot N} \in F(c_1 +_b c_2)$};
(A) edge node[above]{$\psi j_{c_1} i_1$} (B)
(C) edge node[above]{$\psi j_{c_2} o_2$} (B);
where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\H(M \odot N)$:
where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\lH(M \odot N)$:
\node (A) at (0,0) {$H(a_1)$};
\node (B) at (2,0) {$H(c_1+_b c_2)$};
\node (C) at (4,0) {$H(a_2)$};
\node (D) at (2,-0.5) {$\H(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
\node (D) at (2,-0.5) {$\lH(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
(A) edge node[above]{$H(\psi j_{c_1} i_1)$} (B)
(C) edge node[above]{$H(\psi j_{c_2} o_2)$} (B);
where $$\H(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\H$ is given respectively by $\H(M)$ and $\H(N)$:
where $$\lH(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\lH$ is given respectively by $\lH(M)$ and $\lH(N)$:
\node (A) at (0,0) {$H(a_1)$};
\node (B) at (1,0) {$H(c_1)$};
\node (C) at (2,0) {$H(b)$};
\node (D) at (1,-0.5) {$\theta_{c_1} E(d_M)\phi \in F'(H(c_1))$};
\node (E) at (3,0) {$H(b)$};
\node (F) at (4,0) {$H(c_2)$};
\node (G) at (5,0) {$H(a_2)$};
\node (H) at (4,-0.5) {$\theta_{c_2} E(d_N) \phi \in F'(H(c_2))$};
(A) edge node[above]{$H(i_1)$} (B)
(C) edge node[above]{$H(o_1)$} (B)
(E) edge node[above]{$H(i_2)$} (F)
(G) edge node[above]{$H(o_2)$} (F);
Composing these then gives $\H(M) \odot \H(N)$:
Composing these then gives $\lH(M) \odot \lH(N)$:
\node (A) at (0,0) {$H(a_1)$};
\node (B) at (2.25,0) {$H(c_1)+_{H(b)} H(c_2)$};
\node (C) at (4.5,0) {$H(a_2)$};
\node (D) at (2.25,-0.5) {$d_{\H(M) \odot \H(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
\node (D) at (2.25,-0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B);
where $$\hspace{-.4in}\scriptstyle{d_{\H(M) \odot \H(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
We then have a comparison constraint: $$\H_{M,N} \maps \H(M) \odot \H(N) \xrightarrow{\sim} \H(M \odot N)$$given by the globular 2-isomorphism:
where $$\hspace{-.4in}\scriptstyle{d_{\lH(M) \odot \lH(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
We then have a comparison constraint: $$\lH_{M,N} \maps \lH(M) \odot \lH(N) \xrightarrow{\sim} \lH(M \odot N)$$given by the globular 2-isomorphism:
\node (A) at (0,0.5) {$H(a_1)$};
\node (A') at (0,-0.5) {$H(a_1)$};
\node (B) at (2.5,0.5) {$H(c_1)+_{H(b)} H(c_2)$};
\node (C) at (5,0.5) {$H(a_2)$};
\node (C') at (5,-0.5) {$H(a_2)$};
\node (D) at (2.5,-0.5) {$H(c_1 +_b c_2)$};
\node (E) at (7.5,0.5) {$d_{\H(M) \odot \H(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
\node (F) at (7.5,-0.5) {$d_{\H(M \odot N)} \in F'(H(c_1 +_b c_2))$};
\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\H(M) \odot \H(N)}) \to d_{\H(M \odot N)}.$};
\node (E) at (7.5,0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
\node (F) at (7.5,-0.5) {$d_{\lH(M \odot N)} \in F'(H(c_1 +_b c_2))$};
\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\lH(M) \odot \lH(N)}) \to d_{\lH(M \odot N)}.$};
(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B)
(A') edge node [above]{$H(\psi j_{c_1} i_1)$} (D)
(C') edge node [above]{$H(\psi j_{c_2} o_2)$} (D)
(B) edge node [left] {$\kappa^{-1}$} (D);
where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$. The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}. Similarly, for every object $c \in \A$, we have a unit comparison constraint \\[ \H_U \maps U_{\H(c)} \to \H(U_c)\]
given by the globular 2-isomorphism:
where $\kappa$ is the isomorphism 
\[  \kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)\] 
which comes from the finite colimit preserving functor $H \maps \A \to \A'$. The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}. Similarly, for every object $c \in \A$, we have a unit comparison constraint 
\[ \lH_U \maps U_{\lH(c)} \to \lH(U_c)\] 
given by the globular 2-isomorphism:
\node (A) at (0,0.5) {$H(c)$};
\node (A') at (0,-0.5) {$H(c)$};
\node (B) at (1.5,0.5) {$H(c)$};
\node (C) at (3,0.5) {$H(c)$};
\node (C') at (3,-0.5) {$H(c)$};
\node (D) at (1.5,-0.5) {$H(c)$};
\node (E) at (4.5,0.5) {$!_{H(c)} \in F'(H(c))$};
\node (F) at (4.5,-0.5) {$\theta_c E(!_c) \phi \in F'(H(c))$};
(A) edge node[above]{$1$} (B)
(A') edge node [above]{$1$} (D)
(C') edge node [above]{$1$} (D)
where the morphism of decorations is the morphism $\tau \maps !_{H(c)} \to (\theta_c E(!_c) \phi)$ in $F'(H(c))$. These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
\node (A) at (0,0.5) {$(\H(M) \odot \H(N)) \odot \H(P)$};
\node (B) at (0,-0.5) {$\H(M \odot N) \odot \H(P)$};
\node (C) at (0,-1.5) {$\H((M \odot N) \odot P)$};
\node (A') at (3,0.5) {$\H(M) \odot (\H(N) \odot \H(P))$};
\node (B') at (3,-0.5) {$\H(M) \odot \H(N \odot P)$};
\node (C') at (3,-1.5) {$\H(M \odot (N \odot P))$};
(A) edge node[left]{$\H_{M,N} \odot 1$} (B)
(B) edge node[left]{$\H_{M \odot N,P}$} (C)
\node (A) at (0,0.5) {$(\lH(M) \odot \lH(N)) \odot \lH(P)$};
\node (B) at (0,-0.5) {$\lH(M \odot N) \odot \lH(P)$};
\node (C) at (0,-1.5) {$\lH((M \odot N) \odot P)$};
\node (A') at (3,0.5) {$\lH(M) \odot (\lH(N) \odot \lH(P))$};
\node (B') at (3,-0.5) {$\lH(M) \odot \lH(N \odot P)$};
\node (C') at (3,-1.5) {$\lH(M \odot (N \odot P))$};
(A) edge node[left]{$\lH_{M,N} \odot 1$} (B)
(B) edge node[left]{$\lH_{M \odot N,P}$} (C)
(A) edge node[above]{$a$} (A')
(C) edge node [above] {$\H(a')$} (C')
(B') edge node [right] {$\H_{M,N \odot P}$} (C')
(A') edge node [right]{$1 \odot \H_{N,P}$} (B');
(C) edge node [above] {$\lH(a')$} (C')
(B') edge node [right] {$\lH_{M,N \odot P}$} (C')
(A') edge node [right]{$1 \odot \lH_{N,P}$} (B');
\node (A) at (0,0) {$U_{\H(a)} \odot \H(M)$};
\node (B) at (2.5,0) {$\H(U_a) \odot \H(M)$};
\node (C) at (0,-1) {$\H(M)$};
\node (D) at (2.5,-1) {$\H(U_a \odot M)$};
\node (A') at (5,0) {$\H(M) \odot U_{\H(b)}$};
\node (B') at (7.5,0) {$\H(M) \odot \H(U_b)$};
\node (C') at (5,-1) {$\H(M)$};
\node (D') at (7.5,-1) {$\H(M \odot U_b)$};
\node (A) at (0,0) {$U_{\lH(a)} \odot \lH(M)$};
\node (B) at (2.5,0) {$\lH(U_a) \odot \lH(M)$};
\node (C) at (0,-1) {$\lH(M)$};
\node (D) at (2.5,-1) {$\lH(U_a \odot M)$};
\node (A') at (5,0) {$\lH(M) \odot U_{\lH(b)}$};
\node (B') at (7.5,0) {$\lH(M) \odot \lH(U_b)$};
\node (C') at (5,-1) {$\lH(M)$};
\node (D') at (7.5,-1) {$\lH(M \odot U_b)$};
(A) edge node[above]{$\H_U \odot 1$} (B)
(A) edge node[above]{$\lH_U \odot 1$} (B)
(A) edge node[left]{$\lambda$} (C)
(B) edge node[right]{$\H_{U_a,M}$} (D)
(D) edge node[above]{$\H(\lambda')$} (C)
(A') edge node[above]{$1 \odot \H_U$} (B')
(B) edge node[right]{$\lH_{U_a,M}$} (D)
(D) edge node[above]{$\lH(\lambda')$} (C)
(A') edge node[above]{$1 \odot \lH_U$} (B')
(A') edge node[left]{$\rho$} (C')
(B') edge node[right]{$\H_{M,U_b}$} (D')
(D') edge node[above]{$\H(\rho')$} (C');
(B') edge node[right]{$\lH_{M,U_b}$} (D')
(D') edge node[above]{$\lH(\rho')$} (C');
The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}. This shows that $\H=(H,E,\theta)$ is a double functor. Next we show that this double functor is symmetric monoidal. First, that the object component $\H_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits. As for the arrow component $\H_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}. This shows that $\lH=(H,E,\theta)$ is a double functor. Next we show that this double functor is symmetric monoidal. First, that the object component $\lH_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits. As for the arrow component $\lH_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
\node (B) at (1,0) {$c_1$};
\node (D) at (1,-0.5) {$d_{M_1}\in F(c_1)$};
\node (F) at (4,0) {$c_2$};
\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
their tensor product $M_1 \otimes M_2$ in $F\lCsp$ is given by:
\node (B) at (1.5,0) {$c_1+c_2$};
\node (D) at (1.5,-0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
$$d_{M_1 \otimes M_2} \maps 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
and the image of this horizontal 1-cell under the double functor $\H$ is $\H(M_1 \otimes M_2)$ given by:
and the image of this horizontal 1-cell under the double functor $\lH$ is $\lH(M_1 \otimes M_2)$ given by:
\node (A) at (0,0) {$H(a_1+a_2)$};
\node (B) at (2,0) {$H(c_1+c_2)$};
\node (C) at (4,0) {$H(b_1+b_2)$};
\node (D) at (2,-0.5) {$d_{\H(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
\node (D) at (2,-0.5) {$d_{\lH(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
(A) edge node[above]{$H(i_1+i_2)$} (B)
(C) edge node[above]{$H(o_1+o_2)$} (B);
On the other hand, the image of $M_1$ and $M_2$ is given by $\H(M_1)$ and $\H(M_2)$:
On the other hand, the image of $M_1$ and $M_2$ is given by $\lH(M_1)$ and $\lH(M_2)$:
\node (A) at (0,0) {$H(a_1)$};
\node (B) at (1.5,0) {$H(c_1)$};
\node (C) at (3,0) {$H(b_1)$};
\node (D) at (1.5,-0.5) {$d_{\H(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
\node (D) at (1.5,-0.5) {$d_{\lH(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
\node (E) at (4.5,0) {$H(a_2)$};
\node (F) at (6,0) {$H(c_2)$};
\node (G) at (7.5,0) {$H(b_2)$};
\node (H) at (6,-0.5) {$d_{\H(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
\node (H) at (6,-0.5) {$d_{\lH(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
(A) edge node[above]{$H(i_1)$} (B)
(C) edge node[above]{$H(o_1)$} (B)
(E) edge node[above]{$H(i_2)$} (F)
(G) edge node[above]{$H(o_2)$} (F);
and their tensor product $\H(M_1) \otimes \H(M_2)$ is given by:
and their tensor product $\lH(M_1) \otimes \lH(M_2)$ is given by:
\node (A) at (0,0) {$H(a_1)+H(a_2)$};
\node (B) at (2.5,0) {$H(c_1)+H(c_2)$};
\node (C) at (5,0) {$H(b_1)+H(b_2)$};
\node (D) at (2.5,-0.5) {$d_{\H(M_1) \otimes \H(M_2)} \in F'(H(c_1)+H(c_2))$};
\node (D) at (2.5,-0.5) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};
(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
(C) edge node[above]{$H(o_1)+H(o_2)$} (B);
$$\hspace{-.4in} \scriptstyle{d_{\H(M_1) \otimes \H(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \H(M_1) \otimes \H(M_2) \to \H(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
$$\hspace{-.4in} \scriptstyle{d_{\lH(M_1) \otimes \lH(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \lH(M_1) \otimes \lH(M_2) \to \lH(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
\node (A) at (0,0.5) {$H(a_1)+H(a_2)$};
\node (A') at (0,-0.5) {$H(a_1+a_2)$};
\node (B) at (2.5,0.5) {$H(c_1)+H(c_2)$};
\node (C) at (5,0.5) {$H(b_1)+H(b_2)$};
\node (C') at (5,-0.5) {$H(b_1+b_2)$};
\node (D) at (2.5,-0.5) {$H(c_1+c_2)$};
\node (E) at (2.5,1) {$d_{\H(M_1) \otimes \H(M_2)} \in F'(H(c_1)+H(c_2))$};
\node (F) at (2.5,-1) {$d_{\H(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
\node (E) at (2.5,1) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};
\node (F) at (2.5,-1) {$d_{\lH(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
(C) edge node[above]{$H(o_1)+H(o_2)$} (B)
(A) edge node[left]{$\kappa$} (A')
(C) edge node[left]{$\kappa$} (C')
(A') edge node [above]{$H(i_1+i_2)$} (D)
(C') edge node [above]{$H(o_1+o_2)$} (D)
(B) edge node [left] {$\kappa$} (D);
$$\tau_\kappa \maps F'(\kappa)(d_{\H(M_1) \otimes \H(M_2)}) \to d_{\H(M_1 \otimes M_2)}$$

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2020/12/9

@@

\item a functor $H \maps \A \to \A'$ that preserves finite limits,

@@

\item a natural isomorphism $\theta \maps EF \Rightarrow F'H$: 

@@

\item The image of an object $a \in F\lCsp_0=\A$ is the object $H(a) \in F'\lCsp_0=\A'$.

@@

where a decoration morphism $\tau \colon F(h)(x) \to x'$ is mapped to a 
decoration morphism as follows:

@@

@@

\begin{thm}
\label{thm:functoriality}
Given two categories $\A$ and $\A'$ with finite colimits, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a natural isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\Downarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[above]{$F'$} (D);
\end{tikzpicture}
\] 
the triple $(H,E,\theta)$ induces a symmetric monoidal double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
\end{thm}
